Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 architecture.tex
anonymization

  As discussed in the introductory section, in previous work~\cite{vogel2017low} we introduced \tool, a drop-in Python library that allows developers to monitor their Flask-based Python web applications with minimal effort.
%
  The \tool is implemented for Python 3.6 and is available on the Python Package Index repository\footnote{\url{https://pypi.python.org/pypi/flask-monitoring-dashboard/1.8}} from where it can be installed by running \install from the command line. 
%  
  The source code of the \tool is published under a permissive MIT license and is available on GitHub\footnote{\url{https://github.com/flask-dashboard}}.

>>>>

  As discussed in the introductory section, in previous work \withheld we introduced \tool, a drop-in Python library that allows developers to monitor their Flask-based Python web applications with minimal effort.
%
  The \tool is implemented for Python 3.6 and is available on the Python Package Index repository
  % \footnote{\url{https://pypi.python.org/pypi/flask-monitoring-dashboard/1.8}} 
  \footnote{\url{https://pypi.python.org/pypi/[\witheld]}} 
  from where it can be installed by running \install from the command line. 
%  
  The source code of the \tool is published under a permissive MIT license and is available on GitHub\footnote{\url{https://github.com/flask-dashboard}}.

### 2018-04-09 introductory.tex
anonymization

  \zee\footnote{\url{https://github.com/zeeguu-ecosystem/}} is a platform and an ecosystem of applications for accelerating vocabulary acquisition in a foreign language \cite{Lungu16}. 
%
  The architecture of the ecosystem has at its core an API and a series of ecosystem applications that together offer to a learner three main inter-dependent features:

>>>>

  \zee
  % \footnote{\url{https://github.com/zeeguu-ecosystem/}} 
  is a platform and an ecosystem of applications for accelerating vocabulary acquisition in a foreign language \cite{lungu18-chi}. 
%
  The architecture of the ecosystem has at its core an API and a series of ecosystem applications that together offer to a learner three main inter-dependent features:

### 2018-04-09 loc1.tex
nicer benchmarking image
anonymization

  \newpage
  \section{Service Utilization and Performance}
  \label{sec:utilandperf}

@@

  A dashboard can be attached to an already existing Flask application with a single line of code~\cite{vogel2017low} as the following snippet shows\footnote{We do not count the import statement that enables that line.}:

@@

  \va{\Fref{fig:sep} needs to be updated --- it still has 2017 dates}

>>>>

  % \newpage
  \section{Service Utilization and Performance}
  \label{sec:utilandperf}

@@

  A dashboard can be attached to an already existing Flask application with a single line of code \citationwithheld as the following snippet shows\footnote{We do not count the import statement that enables that line.}:

@@
